---
title: "Exploration by Visualization: The Streaming Movies Dataset"
author: "Marina Huang"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: no
    number_sections: no
    dev: pdf
    highlight: tango
  html_document:
    theme: paper
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: no
    smart: yes
    dev: svg
    highlight: tango
    self_contained: true
  github_document:
    toc: true
    toc_depth: 4
    dev: svg
    df_print: kable
    html_preview: false
---

```{r setup, include = FALSE}
# DO NOT ALTER CODE IN THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE, fig.width = 5,
  fig.asp = 0.618, out.width = "80%", dpi = 120,
  fig.align = "center", cache = FALSE
)
# Load packages
suppressPackageStartupMessages(library(tidyverse))
# Load dataset
streaming <- read_csv("streaming.csv")
```

* * *

## Visualization by example

### Histogram of IMDB Scores

```{r}
ggplot(data = streaming) +
  geom_histogram(mapping = aes(x = im_db), bins = 15)
```

This histogram is counting the number of times there is a certain IMDB score. Based on this graph, the score of roughly 6 to 6.5 has the highest number of counts.

### The Difference Between bins and binwidth

```{r}
ggplot(data = streaming) +
  geom_histogram(mapping = aes(x = im_db), bins = 10)
ggplot(data = streaming) +
  geom_histogram(mapping = aes(x = im_db), bins = 20)
```

```{r}
ggplot(data = streaming) +
  geom_histogram(mapping = aes(x = im_db), binwidth = 1)
```

`bins` determines how many bars, or equally spaced intervals there are in the histogram.
Meanwhile, `binwidth` determines the range of the intervals. 


### Histogram of Movies in English vs. Foreign Languages

```{r}
ggplot(data = streaming) +
  geom_histogram(
    mapping=aes(x = im_db, fill = main_language), binwidth = 0.5, alpha = 0.5,
    position = "identity"
  )
```

Adding `fill = main_language` filled the histogram in different colors, distinguished by `main_language`. 
In other words, there are actually 2 histograms shown in one graph, but they two histograms are distinguished by different colors. This definitely changes the way we might interpret the visualization because without the `fill = main_language`, we would not have been able to see that movies with a foreign main language would tend to have higher IMDB scores than movies with English as the main language. 

### Analysis

The shape of the **English** IMDB rating distribution is slightly left skewed with the center being around 6 to 6.5. The shape of the **Foreign** IMDB rating distribution has very left skewed and has the center at around 7. This is a distinguishable difference. This was something I was expecting to see because there have been a lot of foreign movies in the recent years being featured on popular streaming websites, like Netflix. Also, if the ratings of these foreign movies were low, I think American streaming websites would be less inclined to buy the licences to stream the movies.


### Use of alpha = 0.5 and position = "dodge":

```{r}
ggplot(data = streaming) +
  geom_histogram(
    mapping=aes(x = im_db, fill = main_language), binwidth = 0.5, alpha = 0.5,
    position = "dodge"
  )
```

i. Alpha changes the opacity of the histogram.
ii. `position = "identity"` changed the order of the languages displayed on the histogram. The **Foreign** part is now moved to the front instead of behind **English**.
iii. The two language categories do not overlap with `position = "dodge"`.


## Scatterplots

### Correlation Between Rotten Tomato and IMDB Scores

```{r}
ggplot(data = streaming) +
  geom_point(mapping = aes(x = rotten_tomatoes, y = im_db))
```

This plot has a positive trend. This implies that if the Rotten Tomato score of a film is high, then so is the IMDB score of that film.


### Coloring Data Points By Age Rating

```{r}
ggplot(data = streaming) +
  geom_point(mapping = aes(x = rotten_tomatoes, y = im_db, color = age))
```

All of the colors seem to spread out across the plot. There is no age category that would only appear with a specific rating. This tells us that the age variable does not have an effect on how IMBD ratings depend on Rotten Tomatoes ratings.


## Faceting

### IMDB and Rottem Tomato Scores By Streaming Services

```{r}
ggplot(data = streaming) +
  geom_point(mapping = aes(x = rotten_tomatoes, y = im_db)) +
  facet_grid(. ~ streaming)
```

```{r}
ggplot(data = streaming) +
  geom_point(mapping = aes(x = rotten_tomatoes, y = im_db)) +
  facet_grid(streaming ~ .)
```

Adding `facet_grid` divided the plot based on the variable `streaming`. There is a plot for each category under `streaming`. Having `. ~ streaming` displays the category labels horizontally and having `streaming ~ .` displays the category labels aligned vertically. 

## Modeling in `ggplot2`

### Using geom_point and geom_smooth

```{r}
ggplot(data = streaming) +
  geom_point(mapping = aes(x = rotten_tomatoes, y = im_db)) +
  geom_smooth(mapping = aes(x = rotten_tomatoes, y = im_db), method = "lm")
```

The plot follows a positive blue trendline, which matches what I've previously described about the data. The semi-transparent gray region probably represents how well the data points fit the trend. The smaller the gray area is, the better the points in the region fits the trend.


### Adding Axis Titles

```{r}
ggplot(data = streaming) +
  geom_point(mapping = aes(x = rotten_tomatoes, y = im_db, size = 2)) +
  geom_smooth(mapping = aes(x = rotten_tomatoes, y = im_db), method = "lm") +
labs(
  title = "Scatterplot of IMDB vs Rotten Tomatoes Rating",
  x = "Rotten Tomatoes Rating",
  y = "IMDB Rating"
)
```